---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
library(dplyr)
library(ggplot2)
setwd("~/Documents/ReproducibleResearch/Project1")
activity <- read.csv("activity.csv")
dt_activity <- tbl_df(activity)#[complete.cases(activity),])

```


## What is mean total number of steps taken per day?
The total number of steps taken per day is calculated.
```{r totalstepsperday}
totalStepsPerDay <- group_by(dt_activity, date) %>% summarise(Total=sum(steps))
```

A histogram of total number of days is plotted. 
```{r histogram}
hist(totalStepsPerDay$Total)
```

The mean and median total number of steps taken per day are computed.

```{r}
mean(totalStepsPerDay$Total)
median(totalStepsPerDay$Total)
```





## What is the average daily activity pattern?
```{r}
aveStepsPattern <- group_by(dt_activity, interval) %>% summarise(Ave=mean(steps))
p <- qplot(interval, Ave, data=aveStepsPattern, geom="line") +
    ggtitle("Average Daily Activity Pattern") + 
    xlab("Interval") + ylab("Ave Num Steps Taken") +
    geom_vline(xintercept = aveStepsPattern[which.max(aveStepsPattern$Ave),]$interval, 
               color="red", linetype="dotted") #+ 
#    geom_text(aes(aveStepsPattern[which.max(aveStepsPattern$Ave),]$interval, 
#                  aveStepsPattern[which.max(aveStepsPattern$Ave),]$Ave, label="Max"))
print(p)
```


```{r}
aveStepsPattern[which.max(aveStepsPattern$Ave),]$interval
```



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
